---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LevSTR

<!-- badges: start -->
<!-- badges: end -->

The goal of LevSTR is to estimate tandem repeat copy numbers in sequencing data via Levenshtein distance metrics.

## Installation

You can install the development version of LevSTR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Enjewl/Lev-STR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(LevSTR)
## basic example code
Matched_sequence_df <- Lev_repeat_sizer(fastq_example)
head(Matched_sequence_df)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
invisible(LevPlot(Matched_sequence_df, xlim = c(0,100)))
```
