---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LevSTR

<!-- badges: start -->
<!-- badges: end -->

The goal of LevSTR is to estimate tandem repeat copy numbers in sequencing data via Levenshtein distance metrics.

## Installation

You can install the development version of LevSTR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Enjewl/LevSTR")
```

## Running the repeat sizer

The repeat sizer is a simple function that utilizes the [agrep](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/agrep) fuzzy matching to identify reads containing tandem repeats of interest. The following parameters are required:

* **fastq** - Path to fastq file
* **left_flank_seq** - Left side sequence flanking the tandem repeat, example is given for Huntington's disease CAG repeat (i.e., CAAGTCCTTC for Huntington's disease CAG repeat)
* **right_flank_seq** - Right side sequence flanking the tandem repeat, example is given for Huntington's disease CAG repeat (i.e., CAACAGCCGCCACCG for Huntington's disease CAG repeat)
* **repeat_unit_seq** - Sequence of the tandem repeat (i.e., CAG for Huntington's disease)
* **max.distance** - Max Levenshtein distance allowed for match
* **min_n_repeats** - Minimum number of tandem repeats allowed for match (filters out sequences that contain less than this number of repeats)
* **interruptions_repeat_no** - Minimum number of sequential tandem repeats in matched sequence to allow
* **ignore_last_codon** - Ignores the last X number of codons in right flanking sequence to ignore when calculating repeats
* **codon_start** - The codon starting position for matched sequence

```{r example}
suppressPackageStartupMessages(library(LevSTR))

Matched_sequence_df <- Lev_repeat_sizer(
  fastq = fastq_example,
  left_flank_seq = "CAAGTCCTTC",
  right_flank_seq = "CAACAGCCGCCACCG",
  repeat_unit_seq = "CAG",
  max.distance = 0.04,
  min_n_repeats = 10,
  interruptions_repeat_no = 2,
  ignore_last_codon = 1,
  codon_start = 2)
```

## Plotting

Use the LevSTR::LevPlot plotting function to plot a basic histogram.

```{r example-plot}
invisible(LevPlot(Matched_sequence_df, xlim = c(0,100)))
```
