---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LevSTR

<!-- badges: start -->
<!-- badges: end -->

The goal of LevSTR is to estimate tandem repeat copy numbers in sequencing data via Levenshtein distance metrics.

## Installation

You can install the development version of LevSTR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Enjewl/Lev-STR")
```

## Running the repeat sizer

The repeat sizer is a simple function that utilizes the [agrep](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/agrep) fuzzy matching to identify reads containing tandem repeats of interest. The following parameters are required:
* fastq	    Path to fastq file
* left_flank_seq    Left side sequence flanking the tandem repeat, example is given for Huntington's disease CAG repeat
* right_flank_seq   Right side sequence flanking the tandem repeat, example is given for Huntington's disease CAG repeat
* repeat_unit_seq   Sequence of the tandem repeat
* max.distance    Max Levenshtein distance allowed for match
* min_n_repeats   Minimum number of tandem repeats allowed for match (filters out sequences that contain less than this number of repeats)
* interruptions_repeat_no    Minimum number of sequential tandem repeats in matched sequence to allow
* ignore_last_codon   Ignores the last X number of codons in right flanking sequence to ignore when calculating repeats
* codon_start   the codon starting position for matched sequence

```{r example}
invisible(library(LevSTR))
## basic example code
Matched_sequence_df <- Lev_repeat_sizer(fastq_example)
```

## Plotting

Use the LevSTR::LevPlot plotting function to plot a basic histogram.

```{r pressure, echo = FALSE}
invisible(LevPlot(Matched_sequence_df, xlim = c(0,100)))
```
